---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
df<-read.csv(unzip("activity.zip"))
df_complete <- na.omit(df)
```
To calculate the steps per day:
```{r}
df_steps <- aggregate(df_complete$steps, by=list(df_complete$date), sum)$x
```


## What is mean total number of steps taken per day?
```{r}
hist(df_steps, xlab = "steps per day", main = "Histogram of steps")
mean(df_steps)
median(df_steps)
```



## What is the average daily activity pattern?
```{r}
df_intervals <- df[,c(1,3)]
df_steps_intervals <- aggregate(df_intervals, by=list(df_intervals$interval), mean, na.rm=TRUE)
plot(df_steps_intervals$interval, df_steps_intervals$steps , type='l', xlab = "intervals", ylab="median steps")
```

The interval with the maximun number of steps is
```{r}
df_steps_intervals[which.max(df_steps_intervals$steps),]$interval
```


## Imputing missing values
The number of no completed cases (rows with NA values):
```{r}
sum(!complete.cases(df))
```
we'll replace the NA with the mean number of steps in that intervall
```{r}
steps_in_interval <- function(interval, steps){
  if (is.na(steps))
    steps <- round((df_steps_intervals[df_steps_intervals$interval==interval, "steps"]))
   
  return (steps)
}

df2 <- df
df2$steps <- mapply(steps_in_interval, df2$interval, df2$steps)
```

graph on the new data and mean and median
```{r}
df2_steps <- tapply(df2$steps, df2$date, sum)
hist(df2_steps, xlab = "steps per day")
mean(df2_steps)
median(df2_steps)
```

Obviusly the data are different than the original data. We see the Mean bar bigger !


## Are there differences in activity patterns between weekdays and weekends?
